Running faster scripts with DaemonMode.jl

### 2021-10-24 paper/paper.tex
Update results.

All experimental times  were obtained using Julia 1.5.1, with Linux Ubuntu
20.04, and in a computer with 2 CPUs Intel(R) Core(TM) i5-6200U CPU @ 2.30GHz
(using hyper-threading) with 8GB of memory. The version of DaemonMode is v0.1.7.

@@

\begin{table}[htp]
  \centering
  \begin{tabular}{l*{4}{r}}
    \toprule
    Method & \multicolumn{1}{c}{\textbf{hello}} & \multicolumn{1}{c}{\textbf{slow}} & \multicolumn{1}{c}{\textbf{long}} & \multicolumn{1}{c}{\textbf{DS}}\\
    \midrule
    Julia & 0.1486 & 6.5525 &  4.3084 & 20.7313\\
    Julia Client (First) & 0.6464 & 7.0144 & 4.5462 & 19.9024\\
    Julia Client (Next) & 0.4444 & 6.7716 & 4.4853  & 0.4426\\
    Binary Client (First) & 0.2323 & 6.5600 & 4.4720 & 19.7768\\
    Binary Client (Next) & \textbf{0.0283} & \textbf{6.2350} & \textbf{4.2277} & \textbf{0.0430}\\
    \bottomrule
  \end{tabular}
  \caption{Processing time (in seconds) for each problem}
  \label{tab:times}
\end{table}

@@

For programs that load several external packages, like \textbf{DS}, the obtained
improvement is the maximum, thus this is the case in which the scripts benefit
the most. In our example, the time is reduced from 20 seconds to less than 1,
obtaining an final time of 2.1\% of initial time.

@@

There is between 0.2 and 0.3 seconds that are due to the load of the Julia
interpret, so the binary client permits user to avoid that time.

>>>>

All experimental times  were obtained using Julia 1.6.1, with Linux Ubuntu
20.04, and in a computer with 2 CPUs Intel(R) Core(TM) i5-6200U CPU @ 2.30GHz
(using hyper-threading) with 8GB of memory. The version of DaemonMode is v0.1.9.

@@

\begin{table}[htp]
  \centering
  \begin{tabular}{l*{4}{r}}
    \toprule
    Method & \multicolumn{1}{c}{\textbf{hello}} & \multicolumn{1}{c}{\textbf{slow}} & \multicolumn{1}{c}{\textbf{long}} & \multicolumn{1}{c}{\textbf{DS}}\\
    \midrule
    Julia & 0.1592 & 6.8312 &  4.1694 & 16.4286\\
    Julia Client (First) & 0.6886 & 7.9260 & 4.5462 & 16.2308\\
    Julia Client (Next) & 0.6682 & 7.1680 & 4.4853  & 0.6902\\
    Binary Client (First) & 0.5982 & 7.3196 & 4.4720 & 15.4728\\
    Binary Client (Next) & \textbf{0.0130} & \textbf{6.5080} & \textbf{3.5978} & \textbf{0.0410}\\
    \bottomrule
  \end{tabular}
  \caption{Processing time (in seconds) for each problem}
  \label{tab:times}
\end{table}

@@

For programs that load several external packages, like \textbf{DS}, the obtained
improvement is the maximum, thus this is the case in which the scripts benefit
the most. In our example, the time is reduced from 16 seconds to less than 1,
obtaining an final time of 2.1\% of initial time.

@@

There is between 0.6 and 0.7 seconds that are due to the load of the Julia
interpret, so the binary client permits user to avoid that time.
